Drones in Wind

### 2017-08-14 Papers/DroneInTheWind.tex
Update DroneInTheWind.tex

% Load a number of useful packages
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
 \usepackage[margin=1.0in]{geometry}
\usepackage[colorlinks=true]{hyperref}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{float}
\usepackage{float}
\usepackage{enumitem}
\setlist{nosep,after=\vspace{\baselineskip}}
% Two more packages that make it easy to show MATLAB code
\usepackage[T1]{fontenc}
\usepackage[framed,numbered]{matlab-prettifier}
\lstset{
	style = Matlab-editor,
	basicstyle=\mlttfamily\small,
}

@@

\subsubsection{Problem Bounds}
The next step is to set up the \lstinline!problem.bounds!. For the function dynamics, a mass-normalized thrust was chosen to keep the model simple, shown in \textbf{Table 1} below. These parameters were chosen so that results of the simulation can be compared to D'Andrea's paper, \textit{Performance benchmarking of quadrotor systems using time-optimal control}.  \textcolor{red}{Citation}
\begin{figure}[H]
\begin{center}
\begin{tabular}{ |p{2.5cm}||p{2cm}||p{3cm}| }
 \hline
 \multicolumn{3}{|c|}{\textbf{Table 1}   Problem Bounds} \\
 \hline
 Parameter & Value & Description\\
 \hline
 $t_{i}$   & 0 s  & Initial time\\
 $t_{f}$  & 2 s  & Final time\\
 $\underline{F}/m$ & 0 m/$s^{2}$ & Min thrust\\
 $\overline{F}/m$ & 20 m/$s^{2}$ & Max thrust\\
 $\overline{\omega}$ & 10 rad/s & Max pitch rate \\
 \hline
\end{tabular}
\end{center}
\end{figure}

@@

The reason the time grid-spacing is the end-time multiplied by \lstinline!TimeDesnity! is to keep the grid-spacing of the simulation and optimal trajectory path the same. This will be elaborated on a further in \textcolor{red}{Section 4, \textbf{Running Simulation}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                         Running Simulation                                                                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Running Simulation}

@@

Ultimately, the results will be compared to \textbf{one} of D'Andrea's results \textcolor{red}{Citation Needed}.

@@

load data
tsim = processdata.t;
xsim = [processdata.x; processdata.xdot; processdata.z; processdata.zdot;    processdata.theta];
usim = [controllerdata.actuators.pitchrate;...
	controllerdata.actuators.thrust];
\end{lstlisting}
\end{quote}
The preceding lines of code are meant to show how easily the data can be unpacked and plotted against each other. Below, \textcolor{blue}{\textbf{Figure X} shows the optimal and actual state of the quadrotor and \textbf{figure Y} shows the optimal and actual inputs of the quadrotor.}

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{State.png}
    \caption{Quadcopter state over time.}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{Inputs.png}
    \caption{Quadcopter Inputs over time.}
  \end{minipage}
\end{figure}

@@

Before comparing results to D'Andrea's of time optimal trajectory results, the differences in simulations must be addressed. To start, D'Andrea's control input is bang-bang in thrust and bang-singular in pitch rate.\textcolor{red}{Citation Needed}. Additionally, those inputs are non-zero values at both the start and end. Whereas our controller is continuous(\textcolor{red}{???}) and the inputs both begin at zero values. The plot for his results are shown in figure \textcolor{red}{X} below. 
\begin{figure}[H]
\centerline{\includegraphics[width=12cm, height=12cm]{DAndrea_55_Plot.png}}
  \caption{\textcolor{red}{Screenshot?}}
  \label{fig}
\end{figure}
Qualitatively, the inputs can be broken down into sections, as is described by the switching functions \textcolor{red}{Let's try and get another source about this topic}. The Thrust begins at $20 N$, then drops to 0 as the quad-copter nears it's final state, $x=z=5$. The pitch rate begins at $10 rad/s$, drops to $0$, then to $-10 rad/s$ to stabilize, and finally jumps to $10 rad/s$. 
\newline
\newline
In the following subsections we will show how the behavior of our controller compares and how it changes as the final state goes from $x=z=1$ to $x=z=5$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                              D'Andrea Results                                                                        %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% A method that computes quadcopter trajectories satisfying the minimal principle with respect to time-optimality has been developed. The method is based on the two-dimensional quadcopter model with an optimal trajectory created using OptimTraj. By defining the dynamics, bounds and cost function the algorithm was able to create an optimal path for which the drone was to follow. Testing this method, the simulated drone accomplished moving from a position (0,0) to (1,1) in a time optimal manner.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                Future Work                                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Future Work}
With the completion of a 2D optimized drone path, plans to enhance the simulation are underway. Several additions will be added to the current simulation in order to complete this task. Those are as follows 
\newline
\begin{itemize}
  \item Implement 3D rigid body dynamics
  \item Implement additional aerodynamic forces such as drag and ground effect
\end{itemize}
With these immediate goals in mind, an accurate simulation can be created to further test the overarching research initiative.
% Display list of references in IEEE Transactions format.
\clearpage
% Display list of references in IEEE format.
\begin{thebibliography}{9}
\bibitem{OptimTraj} 
MatthewPeterKelly
\textit{OptimTraj}
GitHub
\\\texttt{https://github.com/MatthewPeterKelly/OptimTraj}
\end{thebibliography}

>>>>

% Load a number of useful packages
\usepackage{graphicx}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
 \usepackage[margin=1.0in]{geometry}
\usepackage[colorlinks=true]{hyperref}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{float}
\usepackage{float}
\usepackage{enumitem}
\usepackage[export]{adjustbox}
\setlist{nosep,after=\vspace{\baselineskip}}
% Two more packages that make it easy to show MATLAB code
\usepackage[T1]{fontenc}
\usepackage[framed,numbered]{matlab-prettifier}
\lstset{
	style = Matlab-editor,
	basicstyle=\mlttfamily\small,
}

@@

\subsubsection{Problem Bounds}
The next step is to set up the \lstinline!problem.bounds!. For the function dynamics, a mass-normalized thrust was chosen to keep the model simple, shown in \textbf{Table 1} below. These parameters were chosen so that results of the simulation can be compared to results from D'Andrea's paper\cite{D'Andrea}.
\begin{figure}[H]
\begin{center}
\begin{tabular}{ |p{2.5cm}||p{2cm}||p{3cm}| }
 \hline
 \multicolumn{3}{|c|}{\textbf{Table 1}   Problem Bounds} \\
 \hline
 Parameter & Value & Description\\
 \hline
 $t_{i}$   & 0 s  & Initial time\\
 $t_{f}$  & 2 s  & Final time\\
 $\underline{F}/m$ & 0 m/$s^{2}$ & Min thrust\\
 $\overline{F}/m$ & 20 m/$s^{2}$ & Max thrust\\
 $\overline{\omega}$ & 10 rad/s & Max pitch rate \\
 \hline
\end{tabular}
\end{center}
\end{figure}

@@

The reason the time grid-spacing is the end-time multiplied by \lstinline!TimeDesnity! is to keep the grid-spacing of the simulation and optimal trajectory path the same. This will be elaborated on a further in Section \ref{Running Simulation}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                         Running Simulation                                                                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Running Simulation}\label{Running Simulation}

@@

Ultimately, the results will be compared to \textbf{one} of D'Andrea's results\cite{D'Andrea}.

@@

load data
tsim = processdata.t;
xsim = [processdata.x; processdata.xdot; processdata.z; processdata.zdot;    processdata.theta];
usim = [controllerdata.actuators.pitchrate;...
	controllerdata.actuators.thrust];
\end{lstlisting}
\end{quote}
The preceding lines of code are meant to show how easily the data can be unpacked and plotted against each other. Below, Figure \ref{State Plot} shows the optimal and actual state of the quadrotor, and Figure \ref{Input Plot} shows the optimal and actual inputs of the quadrotor.

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{State.png}
    \caption{\label{State Plot} Quadcopter state over time.}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{Inputs.png}
    \caption{\label{Input Plot} Quadcopter Inputs over time.}
  \end{minipage}
\end{figure}

% \begin{figure}[H]
%   \centering

%     \includegraphics[width=.6\textwidth,left]{State.png}
%     \label{State}
%     \caption{\label{State Plot} Quadcopter state over time.}
%   \end{figure}
%   \hfill
% \begin{figure}[H]
% \label{Input Plot}
%     \includegraphics[width=\textwidth]{Inputs.png}
%     \label{Input Plot}
%     \caption{\label{Input Plot} Quadcopter Inputs over time.}
% \end{figure}

@@

Before comparing results to D'Andrea's of time optimal trajectory results, the differences in simulations must be addressed. To start, D'Andrea's control input is bang-bang in thrust and bang-singular in pitch rate.\textcolor{red}{Citation Needed}. Additionally, those inputs are non-zero values at both the start and end. Whereas our controller is continuous(\textcolor{red}{???}) and the inputs both begin at zero values. The plot for his results are shown in figure \textcolor{red}{X} below. 
\begin{figure}[H]
\centerline{\includegraphics[width=12cm, height=12cm]{DAndrea_55_Plot.png}}
  \caption{\label{D'Andrea Plot} Screenshot of results}
  \label{fig}
\end{figure}
Qualitatively, the inputs can be broken down into sections, as is described by the switching functions \textcolor{red}{Let's try and get another source about this topic}. The Thrust begins at $20 N$, then drops to 0 as the quad-copter nears it's final state, $x=z=5$. The pitch rate begins at $10 rad/s$, drops to $0$, then to $-10 rad/s$ to stabilize, and finally jumps to $10 rad/s$. 
\newline
\newline
In the following subsections we will show how the behavior of our controller compares and how it changes as the final state goes from $x=z=1$ to $x=z=5$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                              D'Andrea Results                                                                        %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% A method that computes quadcopter trajectories satisfying the minimal principle with respect to time-optimality has been developed. The method is based on the two-dimensional quadcopter model with an optimal trajectory created using OptimTraj. By defining the dynamics, bounds and cost function the algorithm was able to create an optimal path for which the drone was to follow. Testing this method, the simulated drone accomplished moving from a position (0,0) to (1,1) in a time optimal manner.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                Future Work                                                                         %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Future Work}
With the completion of a 2D optimized drone path, plans to enhance the simulation are underway. Several additions will be added to the current simulation in order to complete this task. Those are as follows 
\newline
\begin{itemize}
  \item Implement 3D rigid body dynamics
  \item Implement additional aerodynamic forces such as drag and ground effect
\end{itemize}
With these immediate goals in mind, an accurate simulation can be created to further test the overarching research initiative.
% Display list of references in IEEE Transactions format.
\clearpage
% Display list of references in IEEE format.
\begin{thebibliography}{9}
\bibitem{OptimTraj} 
MatthewPeterKelly
\textit{OptimTraj}
GitHub
\\\texttt{https://github.com/MatthewPeterKelly/OptimTraj}

\bibitem{D'Andrea}
D'Andrea

\end{thebibliography}
